Home Nighttime Cough Monitoring

### 2025-03-06 Lilah Melzer/cough_monitor_analysis.qmd
cough monitor tables

@@

```{r results='asis'}
#| label: tbl-mean-demo
#| tbl-cap: Participant characteristics
f <- as.formula(paste0("Diagnosis ~", paste0(colnames(demo), collapse = "+")))
f <- update(f, . ~ . - Diagnosis - sid)
t1 <- tableby(f, data = demo, control = mycontrols)
summary(t1, pfootnote = T)
```

>>>>

demo$nih_race <- droplevels(demo$nih_race)
label(demo$nih_race) <- "Race"

@@

```{r results='asis'}
#| label: tbl-mean-demo
#| tbl-cap: Participant characteristics
t1 <- tableby(Diagnosis ~ nih_sex + age_at_consent + height_perc + weight_perc +
  nih_race + nih_ethnicity + cftr_mod + cftr_mod_type + Genotype + post_fev +
  total_sleep, data = demo, control = mycontrols)
summary(t1, pfootnote = T)
```
